### 2019-10-28 RFCs/HDF5/VOL/vol_internals/internal.tex
Moved existing documentation to new locations.
Former-commit-id: 508462df47bf2580fff47c7ce7bef7fc05c1ab6e

\subsection{Implementing an Internal Plugin}
The first step to implement an internal plugin is to implement all the callbacks defined in the VOL class as described in section~\ref{sec:vol}. After implementing the VOL class, the next step would be to allow users to select
this plugin to be used. This is done by creating a new API routine to
set the plugin on the file access property list. For example, if we
create an internal plugin called ``dummy'' that needs an MPI
communicator and info object as information from the user, that
routine signature should look like:

@@

\subsection{Using an Internal Plugin}
An internal plugin is registered automatically with the HDF5 library when the library gets initialized. Users should not attempt to register an internal plugin. The internal registration operation creates a global identifier for each internal plugin. Applications can query the library for that identifier using the plugin name with {\tt H5VLget\_plugin\_id()}. This identifier is used to initialize the plugin if it requires an initialization phase. A third party library could use that ID to create a plugin that stacks or mirrors on top of an internal plugin using that identifier (refer to section~\ref{sec:stack} for more details on stacking and mirroring).

>>>>

\subsection{Implementing an Internal Plugin}
The first step to implement an internal plugin is to implement all the callbacks defined in the VOL class as described in Section~\ref{sec:vol}. After implementing the VOL class, the next step would be to allow users to select
this plugin to be used. This is done by creating a new API routine to
set the plugin on the file access property list. For example, if we
create an internal plugin called ``dummy'' that needs an MPI
communicator and info object as information from the user, that
routine signature should look like:

@@

\subsection{Using an Internal Plugin}
An internal plugin is registered automatically with the HDF5 library when the library gets initialized. Users should not attempt to register an internal plugin. The internal registration operation creates a global identifier for each internal plugin. Applications can query the library for that identifier using the plugin name with {\tt H5VLget\_plugin\_id()}. This identifier is used to initialize the plugin if it requires an initialization phase. A third party library could use that ID to create a plugin that stacks or mirrors on top of an internal plugin using that identifier (refer to Section~\ref{sec:stack} for more details on stacking and mirroring).

### 2019-10-28 RFCs/HDF5/VOL/vol_internals/intro.tex
Moved existing documentation to new locations.
Former-commit-id: 508462df47bf2580fff47c7ce7bef7fc05c1ab6e

\section{Introduction}
The Virtual Object Layer (VOL) is an abstraction layer in the HDF5
library that intercepts all API calls that could potentially access
objects in an HDF5 container and forwards those calls to plugin
''object drivers''. The plugins could store the objects in variety of
ways. A plugin could, for example, have objects be distributed
remotely over different platforms, provide a raw mapping of the model
to the file system, or even store the data in other file formats (like
native netCDF or HDF4 format). The user still gets the same data model
where access is done to a single HDF5 “container”; however the plugin
object driver translates from what the user sees to how the data is
actually stored. Having this abstraction layer maintains the object
model of HDF5 and would allow HDF5 developers or users to write their
own plugins for accessing HDF5 data.

>>>>

\section{Introduction}
The Virtual Object Layer (VOL) is an abstraction layer in the HDF5
library that intercepts all API calls that could potentially access
objects in an HDF5 container and forwards those calls to the plugin
``object drivers''. The plugins could store the objects in a variety of
ways. A plugin could, for example, have objects be distributed
remotely over different platforms, provide a raw mapping of the model
to the file system, or even store the data in other file formats (like
native netCDF or HDF4 format). The user still gets the same data model
where access is done to a single HDF5 “container”; however, the plugin
object driver translates from what the user sees to how the data is
actually stored. Having this abstraction layer maintains the object
model of HDF5 and would allow HDF5 developers or users to write their
own plugins for accessing HDF5 data.
